Local Spectral Clustering of Density Upper Level Sets

### 2019-01-19 icml/icml_local_density_clustering.tex
added theorem for non-convex setting

	\item
	\label{asmp: cluster_diameter}
	\textit{Cluster diameter:}
	There exists $D < \infty$ such that for all $x, x' \in \Csig$:
	\begin{equation*}
	\norm{x - x'} \leq D,
	\end{equation*}
	and \textcolor{red}{$\Csig$ is a convex set.}
\end{enumerate}

@@

We now provide an upper bound for $\Psi_{n,r}(\Cset[\Xbf])$.
\begin{theorem}
	\label{thm: inverse_mixing_time_lower_bound}
	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$. Then, for any $r < \sigma/4d$, the following statement holds: with probability one
	\begin{align}
	\label{eqn: inverse_mixing_time_lower_bound}
	\liminf_{n \to \infty} & \Psi_{n,r}(\Csig[\Xbf]) \geq \nonumber \\ & c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu + c_{\lambda}) \biggl( c_{\lambda}(d^3 \log\mu + c_2) + \nonumber \\
	& \frac{d^2D^2}{r^2} \bigl( \log d + c_2 \frac{d^2D^2}{r^2} \frac{\Lambda_{\sigma}^{2}}{\lambda_{\sigma}^{2}}c_{\lambda} + \nonumber \\
	& c_3  + \log \log \mu \bigr) \biggr),
	\end{align}
	where $\mu = \log(\frac{2D}{r})$, $c_1 = 3852800/3$, $c_2 = 331776$, and $c_3 = \log 2$ are all dimension free, and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$. 
\end{theorem}

>>>>

	\item
	\label{asmp: cluster_diameter}
	\textit{Cluster diameter:}
	There exists $D < \infty$ such that for all $x, x' \in \Csig$:
	\begin{equation*}
	\norm{x - x'} \leq D.
	\end{equation*}
\end{enumerate}

@@

We now provide a lower bound for $\Psi_{n,r}(\Cset[\Xbf])$.

\begin{theorem}
	\label{thm: inverse_mixing_time_lower_bound_nonconvex}
	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$. Then, for any $r < \sigma/4d$, the following statement holds with probability at least $1 - \delta$: Fix $\epsilon > 0$. Then, for 
	\begin{equation*}
	n \geq ??
	\end{equation*}
	we have
	\begin{align}
	\label{eqn: inverse_mixing_time_lower_bound_nonconvex}
	1 / \Psi_{n,r}(\Csig[\Xbf]) & \leq \left(d \log \mu + c_{\lambda} \right) \cdot \nonumber \\ 
	& \left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d \log \mu + c_{\lambda}\right)\right)
	\end{align}
	where $\mu = \log(\frac{2D}{r})$, $c_1 = 19264000/3$, $c_2 = 331776$, and $c_3 = 128 9^d c_1/5 \cdot (1 + \epsilon)^4/(1 - \epsilon)^4$ are constants which depend only on dimension, and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$. 
\end{theorem}

\begin{theorem}
	\label{thm: inverse_mixing_time_lower_bound}
	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$. Then, for any $r < \sigma/4d$, the following statement holds: with probability one
	\begin{align}
	\label{eqn: inverse_mixing_time_lower_bound}
	\liminf_{n \to \infty} & \Psi_{n,r}(\Csig[\Xbf]) \geq \nonumber \\ & c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu + c_{\lambda}) \biggl( c_{\lambda}(d^3 \log\mu + c_2) + \nonumber \\
	& \frac{d^2D^2}{r^2} \bigl( \log d + c_2 \frac{d^2D^2}{r^2} \frac{\Lambda_{\sigma}^{2}}{\lambda_{\sigma}^{2}}c_{\lambda} + \nonumber \\
	& c_3  + \log \log \mu \bigr) \biggr),
	\end{align}
	where $\mu = \log(\frac{2D}{r})$, $c_1 = 3852800/3$, $c_2 = 331776$, and $c_3 = \log 2$ are all dimension free, and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$. 
\end{theorem}
